GSoC 2014 info session - phpMyAdmin

### 2014-02-26 phpmyadmin/GSoC_infosession_05Mar2014/presentation.tex
update links, dates and ideas to 2014

      \item to get new features implemented in future versions

@@

@@

    \frametitle{Ideas list for GSoC 2013}
    Full list : \href{http://wiki.phpma.org/pma/GSoC\_2013\_Ideas\_List}{wiki.phpma.org/pma/GSoC\_2013\_Ideas\_List}

@@

      \item refactoring
      \item synchronize data
      \item AJAX error reporting
      \item interface improvements

@@

      \item application deadline : May 3
      \item patch deadline (phpMyAdmin) : May 10

@@

    \textbf{May 27} - When you get selected :

@@

      \item community bonding period : get up to speed, read, ask questions, set up your wiki, clone the git repo, Google administration
      \pause
      \item \textbf{June 17} - start coding, first payment

@@

      \pause
      \item \textbf{August 2} - mid-term evaluation, based on your schedule + payment
      \pause
      \item finish coding, documentation, testing
      \pause
      \item \textbf{September 16} - pencils down, final evaluation, submit code, final payment

@@

      \item GSoC info : \href{http://wiki.phpma.org/pma/GSoC\_2013\_Applicant\_Guide}{wiki.phpma.org/pma/GSoC\_2013\_Applicant\_Guide}

>>>>

      \item get new features implemented in future versions

@@

      \item 2013 : 6 students, 6 passed -> phpMyAdmin 4.1

@@

    \frametitle{Ideas list for GSoC 2014}
    Full list : \href{http://wiki.phpma.org/pma/GSoC\_2014\_Ideas\_List}{wiki.phpma.org/pma/GSoC\_2014\_Ideas\_List}

@@

      \item (user) interface improvements
      \item Error reporting
      \item structure tools 
        \item database normalization
        \item central list of columns

@@

      \item \textbf{March 21st} : application deadline
      \item \textbf{March 28th} : patch deadline (phpMyAdmin)

@@

    When you get selected :

@@

      \item community bonding period : get up to speed, read, ask questions, set up your wiki, clone the git repo, Google 

@@

@@

      \item GSoC info : \href{http://wiki.phpma.org/pma/GSoC\_2014\_Applicant\_Guide}{wiki.phpma.org/pma/GSoC\_2014\_Applicant\_Guide}
